---
title: "Parameter Estimation"
author: "최규빈"
header-includes:
- \usepackage{kotex}
- \usepackage{caption}
- \usepackage{amsthm} 
- \usepackage{amsmath, amsfonts, amssymb} 
- \usepackage{enumerate} 
- \usepackage{cite}
- \usepackage{algpseudocode}
- \usepackage{algorithm}
- \usepackage{indentfirst}
- \usepackage{bm}
- \DeclareMathOperator*{\argmin}{arg\,min}
- \DeclareMathOperator*{\argmax}{arg\,max}
- \usepackage{booktabs}
- \usepackage{animate}
- \usepackage{algpseudocode}
- \usepackage{algorithm}
- \usepackage{amsthm}
- \usepackage{graphicx,lscape}
- \usepackage{subcaption}
- \usepackage{xcolor}
- \linespread{2}
fontsize: 11pt
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

$$x^2$$

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
